`conmat`: generate synthetic contact matrices for a given age-stratified population

### 2025-03-04 paper/paper.qmd
some minor tweaks to get GH actions to build PDF appropriately for JOSS submission

---
title: '`conmat`: generate synthetic contact matrices for a given age-stratified population'
authors:
- affiliation: 1
  name: Nicholas Tierney
  orcid: 0000-0003-1460-8722
- affiliation: 1,3
  name: Chitra Saraswati
  orcid: 0000-0002-8159-0414
- affiliation: 1,3
  name: Aarathy Babu
  orcid: 
- affiliation: 4
  name: Michael Lydeamore
  orcid: 0000-0001-6515-827X
- affiliation: 1,2
  name: Nick Golding
  orcid: 0000-0001-8916-5570
date: today
bibliography: references.bib
cite-method: biblatex
tags:
- epidemiology
- R
- infectious disease
affiliations:
- index: 1
  name: Telethon Kids Institute
- index: 2
  name: Curtin University
- index: 3
  name: 
- index: 4
  name: Monash University
execute: 
  echo: true
  cache: false
format: 
  html: 
    keep-md: true
    fig-height: 4
    fig-align: center
    fig-format: png
    dpi: 300
---

@@

We can plot the resulting contact matrix for Tasmania with `autoplot`, shown in @fig-autoplot-contacts.

@@

These covariates capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix). The key features of the relationship between the age groups, represented by spline transformations of the six covariates, are displayed in @fig-show-partial-plots for the home setting. The spline-transformed $|i-j|$ and $|i-j|^{2}$ terms give the strong diagonal lines modelling people generally living with those of similar age and the intergenerational effect of parents and (faintly) grandparents with children. The spline-transformed $\text{max}(i, j)$ and $\text{min}(i, j)$ terms give the higher rates of at-home contact among younger people of similar ages and with their parents.

>>>>

---
title: '`conmat`: generate synthetic contact matrices for a given age-stratified population'
authors:
- affiliation: 1
  name: Nicholas Tierney
  orcid: 0000-0003-1460-8722
- affiliation: 1,3
  name: Chitra Saraswati
  orcid: 0000-0002-8159-0414
- affiliation: 1,3
  name: Aarathy Babu
  orcid: 
- affiliation: 4
  name: Michael Lydeamore
  orcid: 0000-0001-6515-827X
- affiliation: 1,2
  name: Nick Golding
  orcid: 0000-0001-8916-5570
date: today
bibliography: paper.bib
cite-method: biblatex
tags:
- epidemiology
- R
- infectious disease
affiliations:
- index: 1
  name: The Kids Research Institute Australia, WA, Australia
- index: 2
  name:  University of Western Australia, WA, Australia
- index: 3
  name: Monash University, VIC, Australia
execute: 
  echo: true
  cache: false
format: 
  html: 
    keep-md: true
    fig-height: 4
    fig-align: center
    fig-format: png
    dpi: 300
---

@@

We can plot the resulting contact matrix for Tasmania with `autoplot`, shown in (Figure \ref{fig-autoplot-contacts}).

@@

These covariates capture typical features of inter-person contact, where individuals primarily interact with people of similar age (the diagonals of the matrix), and with grandparents and/or children (the so-called 'wings' of the matrix). The key features of the relationship between the age groups, represented by spline transformations of the six covariates, are displayed in Figure \ref{fig-show-partial-plots} for the home setting. The spline-transformed $|i-j|$ and $|i-j|^{2}$ terms give the strong diagonal lines modelling people generally living with those of similar age and the intergenerational effect of parents and (faintly) grandparents with children. The spline-transformed $\text{max}(i, j)$ and $\text{min}(i, j)$ terms give the higher rates of at-home contact among younger people of similar ages and with their parents.
